### 2015-05-15 corral.tex
fixes

\whoop is a sound but imprecise static data race analyzer. For developers who deem false alarms as unacceptable, we consider a method for leveraging the full or partial race-freedom guarantees provided by \whoop to accelerate the performance of \corral~\cite{lal2012corral}, a precise bug-finder used by Microsoft to analyze Windows drivers~\cite{lal2014powering}.  Because \corral operates on Boogie programs, it was easy to integrate it into our toolchain (see Figure~\ref{fig:whoop} -- C). Our technique, though, is general and capable in principle of accelerating any concurrency bug-finder that operates by interleaving threads at shared memory operations.

>>>>

\whoop is a sound but imprecise static race analyzer. For developers who deem false alarms as unacceptable, we consider a method for leveraging the full or partial race-freedom guarantees provided by \whoop to accelerate \corral~\cite{lal2012corral}, a precise bug-finder used by Microsoft to analyze Windows drivers~\cite{lal2014powering}.  Because \corral operates on Boogie programs, it was easy to integrate it into our toolchain (see Figure~\ref{fig:whoop} -- C). Our technique, though, is general and capable in principle of accelerating any concurrency bug-finder that operates by interleaving threads at shared memory operations.

### 2015-05-15 whoop.tex
fixes

Statically analyzing drivers requires to ``close'' the environment by abstracting away the low-level implementation details. To this end, we developed a simple model for the Linux kernel that consists of (nondeterministic) stub functions. A limitation of our model is that it can, and will, ultimately result in false positives. However, we currently only focus on finding data races, and thus can get away with over-approximating a lot of the underlying kernel functionality, without losing too much precision. Making our model more precise is an ongoing manual effort, but requires Linux expertise. We argue that further work on the model is orthogonal to the contributions of this paper. Also, even if our symbolic analysis results in false positives, \whoop can still use the results to significantly speedup a more precise bug-finder, as seen in \S\ref{corral} and \S\ref{evaluation}.

>>>>

Statically analyzing drivers requires ``closing'' the environment by abstracting away the low-level implementation details. To this end, we developed a simple model for the Linux kernel that consists of (nondeterministic) stub functions. A limitation of our model is that it can, and will, ultimately result in false positives. However, we currently only focus on finding data races, and thus can get away with over-approximating large parts of the underlying kernel functionality, without losing too much precision. Making our model more precise is an ongoing manual effort, but requires Linux expertise. We argue that further work on the model is orthogonal to the contributions of this paper. Also, even if our symbolic analysis results in false positives, \whoop can still use the results to significantly speedup a more precise bug-finder, as seen in \S\ref{corral} and \S\ref{evaluation}.
